### 2022-06-21 README.Rmd
el_mean() arguments order changed.

# melt - Multiple Empirical Likelihood Tests
<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/markean/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/markean/melt?branch=master)
<!-- badges: end -->

>>>>

# melt - Multiple Empirical Likelihood Tests
<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/markean/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/markean/melt?branch=master)
<!-- badges: end -->
